A user-extensible and adaptable parser architecture

### 2008-06-02 papers/sgai-2008/paper.tex
Improved the SMTP footnote so it isn't referenced twice.

The architecture described herein was developed as part of a larger project
to improve anti-spam techniques by analysing the performance of the set of
filters currently in use, optimising the order and membership of the set
based on that analysis, and developing supplemental measures where there is
a deficiency.  Most anti-spam techniques are
content-based~\cite{a-plan-for-spam, word-stemming, relaxed-online-svms},
which requires accepting the mail in the first place, but rejecting is
preferable in many cases: senders of non-spam mail that is mistakenly
rejected will receive an immediate non-delivery notice; load is reduced on
mail servers (allowing more intensive content-based measures to be used);
users have less mail to wade through.  Improving the performance of
anti-spam measures which are applied when mail is being transferred via
SMTP\footref{smtp footnote} is the goal of this project, by providing a
platform for reasoning about anti-spam filters.  The approach chosen to
measure performance was to analyse the log files produced by the mail
server, rather than modifying the mail server to generate performance
statistics; this approach improves the chances of other sites testing and
utilising the software.  The need arose for a parser capable of dealing
with the great number and variety of log lines produced by
Postfix~\cite{postfix}, the SMTP\footnote{\label{smtp footnote}Simple Mail
Transfer Protocol transfers mail across the Internet.  It is a simple,
human readable, plain text protocol, making it quite easy to test and debug
problems with it.  The original protocol definition is
RFC~821~\cite{RFC821}, updated in RFC~2821~\cite{RFC2821}.} server in use.
The parser must be designed so that adding support for parsing new log
lines is a simple task, as the log lines will continue to evolve over time.
The variety in log lines occurs for several reasons:

>>>>

The architecture described herein was developed as part of a larger project
to improve anti-spam techniques by analysing the performance of the set of
filters currently in use, optimising the order and membership of the set
based on that analysis, and developing supplemental measures where there is
a deficiency.  Most anti-spam techniques are
content-based~\cite{a-plan-for-spam, word-stemming, relaxed-online-svms},
which requires accepting the mail in the first place, but rejecting is
preferable in many cases: senders of non-spam mail that is mistakenly
rejected will receive an immediate non-delivery notice; load is reduced on
mail servers (allowing more intensive content-based measures to be used);
users have less mail to wade through.  Improving the performance of
anti-spam measures which are applied when mail is being transferred via
SMTP\footnotemark{} is the goal of this project, by providing a platform
for reasoning about anti-spam filters.  The approach chosen to measure
performance was to analyse the log files produced by the mail server,
rather than modifying the mail server to generate performance statistics;
this approach improves the chances of other sites testing and utilising the
software.  The need arose for a parser capable of dealing with the great
number and variety of log lines produced by Postfix~\cite{postfix}, the
SMTP server in use.  The parser must be designed so that adding support for
parsing new log lines is a simple task, as the log lines will continue to
evolve over time.  The variety in log lines occurs for several
reasons:\footnotetext{Simple Mail Transfer Protocol transfers mail from
sender to one or more recipients across the Internet.  It is a simple,
human readable, plain text protocol, making it quite easy to test and debug
problems with it.  The original protocol definition is
RFC~821~\cite{RFC821}, updated in RFC~2821~\cite{RFC2821}.}
